### 2022-07-07 main.tex
done

\section*{Discussion}

In summary, using a series of simplified models, we have shown that asymptomatic infections (including the more general category of non-symptomatic transmissions) can represent a double-edged sword by providing a better outcome for many individuals while facilitating onward transmission that leads to a worse outcome for the population as a whole.
Extending our framework further shows that the immunity profile plays a critical role in determining the dynamics of future variant. 
For example, while protection against symptoms (but not against transmission) protects health at the individual level, it can lead to more infections, and potentially more deaths, at the population level \swp{JSW: what's the Koelle and Lopman paper about vaccination that you were thinking?}.

@@

>>>>

@@

In summary, using a series of simplified models, we have shown that asymptomatic infections (including the more general category of non-symptomatic transmissions) can represent a double-edged sword by providing a better outcome for many individuals while facilitating onward transmission that leads to a worse outcome for the population as a whole.
Extending our framework further shows that the immunity profile plays a critical role in determining the dynamics of future variant. 
For example, while protection against symptoms (but not against transmission) protects health at the individual level, it can lead to more infections, and potentially more deaths, at the population level.
Similar concern was raised in prioritizing vaccine choices that could reduce severe outcomes vs. others that could reduce transmission \citep{koelle2022changing}.
